---
title: "Potential Errors"
output: html_document
authors: "Bailie Wynbelt, Hailey Park, Zoe Evans, Josie Graydon"
date: "2023-04-11"
---

## This file contains a list of potential errors that could happen when running the script

### GGPLOT ERRORS 

# If ggplot is not working run the following before running the ggplot code for future and current sdm, otherwise this is not needed. This function closes the specified plot (by default the current device).

```{r}
dev.off() 
```

### CURRENT AND FUTURE SDM ERRORS

# The following code results in a warning message, this is okay! Do not worry.

```{r}
currentEnv <- getData("worldclim", var="bio", res=2.5, path="data/") 
```

# Warning message:
```{r}
In getData("worldclim", var = "bio", res = 2.5, path = "data/") : 
getData will be removed in a future version of raster 
Please use the geodata package instead
```

# The following lines of code are RAM heavy, make sure to run these individually and wait until they appear in the environment to continue.

```{r}
occEnv <- na.omit(raster::extract(x = clim, y = snailDataNotCoords))

absenceEnv<- na.omit(raster::extract(x = clim, y = backgroundPoints))
```

# The following line of code could result in the following error
```{r}
snailSDM <- dismo::maxent(x = presenceAbsenceEnvDf, 
                          p = presenceAbsenceV, 
                          path=paste("output/maxent_outputs"), )
```

#Error in .jcheck(silent = TRUE) :
```{r}
No running JVM detected. Maybe .jinit() would help.
```

#This means that Java is no longer working in R, to help solve this issue go to "Session", "Clear Workspace", and restart R. You might need to do this everytime you run the code.

